Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
revise abstract (still <170)

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
% PPA
The ``parahippocampal place area'' (PPA)
is a visual area in the human ventral stream with increased hemodynamic
activity correlated with the perception of landscape photos compared to faces or objects.
% AV, AD: operationalization
Here we investigate the perception of
spatial information in 14 individuals from the open-data resource \textit{studyforrest.org}
that were watching a two-hour Hollywood
movie and listened to the movie's audio-description.
% auditory localizer?
%in order to explore if a naturalistic auditory narrative could be used
%to localize a ``visual area''.
% GLM
We model hemodynamic activity based on annotations of selected stimulus features,
% VIS
and compare results to a block-design visual localizer.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, a movie stimulus is associated with
increased activation spatially overlapping with a traditionally
localized PPA.
% results: group AD
In contrast, activation for an auditory stimulus is more restricted
to the anterior PPA.
% results: individual AD
On an individual level, hemodynamic responses
form bilateral clusters in the PPA of nine individuals and unilateral
clusters in another two.
% conclusion: generalizability
Results suggest that activation in the PPA generalizes beyond
pictures of landscapes to spatial information embedded in
a naturalistic movie and even an auditory narrative, and may
% conclusion: PPA has subregions
call for considering a functional subdivision of the PPA.
\end{abstract}

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations \citep{haeusler2016cutanno} in the audio-visual
movie ``Forrest Gump'', while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech \citep{hausler2021studyforrest} occurring in the movie's
audio-description.
% GLM contrasts
We applied whole-brain, model-based, mass-univariate analyses to a series of
datasets with BOLD fMRI data from naturalistic and conventional block-design
stimulation from the same set of participants, available from the open-data
resource \href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
\todo{cite Häusler \& Hanke 2021}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  PPA
The ``parahippocampal place area'' (PPA) in the human ventral visual stream
exhibits increased hemodynamic activity correlated with the perception of
landscape photos compared to faces or objects.
% AV, AD: operationalization
Here, we investigate the perception of spatial information in 14 individuals
watching a two-hour Hollywood movie and listening to the movie's
audio-description as part of the open-data resource \textit{studyforrest.org}.
% auditory localizer?
%in order to explore if a naturalistic auditory narrative could be used to
%localize a ``visual area''.  GLM
We model hemodynamic activity based on annotations of selected stimulus
features,
% VIS
and compare results to a block-design visual localizer.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, increased activation correlating with spatial information
occcuring in the movie is overlapping with a traditionally localized PPA.
% results: group AD
Activation correlating with semantic spatial information occurring in the
audio-description is more restricted to the anterior PPA.
% results: individual AD
On an individual level, we find signficant bilateral activity in the PPA
of nine individuals and unilateral activity in one individual.
% conclusion: generalizability
Results suggest that activation in the PPA generalizes to spatial information
embedded in a movie and spatial information in an auditory narrative, and may
% conclusion: PPA has subregions
call for considering a functional subdivision of the PPA.  \end{abstract}

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump''
\citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{hausler2021studyforrest}.
% GLM contrasts
We applied whole-brain, model-based, mass-univariate analyses to a series of
datasets with BOLD fMRI data from naturalistic and conventional block-design
stimulation from the same set of participants, available from the open-data
resource \href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
